First steps with blogdown

### 2021-10-15 text/Rmd/first-steps-with-blogdown/index.Rmd
Finished updating 03 files

![Dialog box for project type](first-steps-with-blogdown-03.png)

@@

>>>>

![Dialog box for project type](http://www.pmean.com/new-images/21/first-steps-with-blogdown-03.png)

@@

![Preview website main page](http://www.pmean.com/new-images/21/first-steps-with-blogdown-04.png)
![Preview website main page](http://www.pmean.com/new-images/21/first-steps-with-blogdown-05.png)

![Preview website main page](http://www.pmean.com/new-images/21/first-steps-with-blogdown-06.png)

![Preview website main page](http://www.pmean.com/new-images/21/first-steps-with-blogdown-07.png)
